---
title: "Stock Prices"
author: "Trevor"
date: "8 November 2019"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Stock Market 

- The stock market is driven by simply supply and demand
- The more demand for a stock, the higher the price


## Application Overview

- This application plots a certain stock given the predefined observation period
- Prices are obtained by yahoo finance
- The app also allows for the stock prices to be plotted on the log scale

## Instructions

- Put in the ticker symbol. These can be looked up at:
https://finance.yahoo.com/lookup/

- Use the slider to pick the observation period
- Tick the bos if you want to view the y-axis on the log scale

## Data of BHP stock

```{r BHP, echo = TRUE, warning=FALSE, message=FALSE}
library(quantmod)

getSymbols("BHP", src = "yahoo", 
           from = as.Date("2006-01-01"),
           to = as.Date("2019-10-31"))

head(BHP)
```


